HCI Draft Paper

### 2015-11-30 sigchi-latex-proceedings 2/draft-paper.tex
appendix E

What is your gender? (choose one)\\
* Male\\
* Female\\
* Trans*\\
* Other\\

Are you: (choose one)\\
* Right-handed\\
* Left-handed\\
* Ambidextrous\\

Have you used the Android operating system before? (choose one)\\
* Yes\\
* No\\

Do you own an Android phone? (choose one)\\
* Yes\\
* No\\

What version of Android are you most comfortable with? (choose one)\\
* KitKat\\
* Lollipop\\
* Marshmallow\\
* I’m not sure\\
* Other\\

@@

>>>>

What is your gender? (choose one)\\
* Male\\
* Female\\
* Trans*\\
* Other

Are you: (choose one)\\
* Right-handed\\
* Left-handed\\
* Ambidextrous

Have you used the Android operating system before? (choose one)\\
* Yes\\
* No

Do you own an Android phone? (choose one)\\
* Yes\\
* No

What version of Android are you most comfortable with? (choose one)\\
* KitKat\\
* Lollipop\\
* Marshmallow\\
* I’m not sure\\
* Other

@@

\section{Appendix E: Exit Survey}
With what speed did you perceive you were able to switch between applications?\\
KitKat (Non-stacked)\\
* Sluggish\\
* Slow\\
* Average\\
* Fast\\
* Lightning Fast

Lollipop(Stacked)\\
* Sluggish\\
* Slow\\
* Average\\
* Fast\\
* Lightning Fast\\

With what accuracy did you perceive you were able to switch between applications?\\
KitKat (Non-stacked)\\
* Terrible accuracy\\
* Not very accurate\\
* Average\\
* Fairly accurate\\
* Got it every time

Lollipop(Stacked)\\
* Terrible accuracy\\
* Not very accurate\\
* Average\\
* Fairly accurate\\
* Got it every time\\

Do you have a preference on using either OS for its multitasking interface?\\
* KitKat (Non-stacked)\\
* Lollipop (Stacked)\\
* No preference\\
